\sectionTitle{Professional Experiences}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Current}   
    	{Ford Motor Company | Full Stack Developer}{Dearborn}{MI} % company, title, location
    {Jan 2018} {
        			\textbullet \thinspace Developing software delivery mechanism for OTA (over the air) updates for vehicles. \\
			 \textbullet \thinspace Constantly involving in architectural re-design due to growth and new features. \\
           		\textbullet \thinspace Created \texttt{4} out of \texttt{6} well tested micro-serivces, using  spring initializr. \\
           		 \textbullet \thinspace Applied \textbf{TDD} approach from the beginning and achieved a code coverage of \texttt{95\%-91\%} for all micro-services.\\
			 \textbullet \thinspace First in department to use queues (\textbf{Service bus, Kafka }), as a consumer and producer using only spring libraries; thereby keeping implementation agnostic.\\
			 \textbullet \thinspace Used streaming solutions for large file upload/download as part of request. To keep application running out of memory, and never to have memory leaks as well. \\
			 \textbullet \thinspace Paired  across teams to build Angular based UI, that servers as a AppStore-esque web-based application.\\
			\textbullet \thinspace Scripted \textbf{Jenkins} pipeline to include release as stage that publishes to private nexus repo.\\
            		 \textbullet \thinspace Mentored \texttt{3} developers on the team at various level of the project. 
		       }
			{Liquidbase, Spring 2.0, TDD, (CI) Git, (CD) Jenkins, Nexus, PCF, MS-SQL (Azure), Angular 6} %tags
  \emptySeparator
   \experience
    {Dec 2017}  
    	{Ford Motor Company | Software Engineer}{Dearborn}{MI} % company, title, location
    {May 2017} {
                     \textbullet \thinspace	Brought up new backend micro-services that help create profiles for electric vehicle's charge stations based on location. \\
			 \textbullet \thinspace Created Integrated and Functional Test suite for feature traceability and valued added user stories. \\
			 \textbullet \thinspace Integrated with third part APIs to get location information, that is in turn used in creating user profiles. \\
			\textbullet \thinspace Designed a three layer data model to have complete de-coupling, and achieve abstraction for development. 
                       }
                    {Spring Boot, Gradle, Lombok, Mapstruct,  BDD, Gherkin,  PCF, Mongo Db} %tags
  \emptySeparator
  
  \experience
    {April 2017} 
    	{Cerner | Java Developer}{Kansas City}{MO} % company, title, location
    {September 2014} {
                      		\textbullet \thinspace Added new features for scalable applications that register and schedule patient visits across various hospitals/clinics in USA. \\
		 		 \textbullet \thinspace Worked on SOA based application for patient data management. Implemented services to meet compliance by HIPAA. \\
				 \textbullet \thinspace Implemented persistence layer using Hibernate to retrieve and store data from tables in Oracle. \\
				 \textbullet \thinspace Migrated \texttt{1000+} of lines of code (about 20\%) to use spring from Java 6. \\ 
				 \textbullet \thinspace Developed Python scripts for automating tests based on given test plans, these scripts would read i/p and run them against tests and dump o/p in target folder.	 
		                 }
		                  {JPA, Hibernate, Spring Data, Maven, Python, SVN } %tags
  \emptySeparator
  \experience
    {March 2014}  
    	{Qualcomm Semiconductors  | CPU Verification Engineer}{Raleigh}{NC} % company, title, location
    {April 2013} {
        		\textbullet \thinspace	Architecture verification of the CPU of the then next-gen Qualcomm's ARMv8 and ARMv7 compliant processor. \\
			 \textbullet \thinspace Developed tests to verify ICACHE commands in ARM architecture. \\
		 \textbullet \thinspace Provided solutions to bridge OVM/UVM (different verification methodologies) based test suite with DV(design verification) team's test bench.\\
		 \textbullet \thinspace Created new OVM/UVM based components new design to ensure functional coverage. \\
		 \textbullet \thinspace Wrote functional verification tests for 64-bit ARM based processor based on specifications.
		       }
		      {Java, Matlab, VHDL, Verilog, Perl, Cadence} %tags
\end{experiences}
